---
title: "Business Intelligence Lab Submission Markdown"
author: "<Specify your group name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** | *\<list one Student name, class group (just the letter; A, B, or C), and ID per line, e.g., 123456 - A - John Leposo; you should be between 2 and 5 members per group\>* |
|                                                   |                                                                                                                                                                          |
|                                                   | 1.  128998 - B - Crispus Nzano                                                                                                                                            |
|                                                   |                                                                                                                                                                          |
|                                                   | 2.  134100 - B - Timothy Obosi                                                                                                                                             |
|                                                   |                                                                                                                                                                          |
|                                                   | 3.  134092 - B - Alison Kuria                                                                                                                                                                                                                                                 |
|                                                   |                                                                                                                                                                          |
|                                                   | 4.  135269 - B - Clifford Kipchumba                                                                                                                          |
|                                                   |                                                                                                                                                      |
|                                                   | 5.  112826 - B - Matu Ngatia                                                                                                                          |
|                                                   |                                                  
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   | Team Kubwa                                                                                                       |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                                                                                                  |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                                                                                                 |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                                                                                               |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

# Setup Chunk

We start by installing all the required packages

```{r Install Packages, echo=TRUE, message=FALSE, warning=FALSE}
## formatR - Required to format R code in the markdown ----
if (!is.element("formatR", installed.packages()[, 1])) {
  install.packages("formatR", dependencies = TRUE,
                   repos="https://cloud.r-project.org")
}
require("formatR")


## readr - Load datasets from CSV files ----
if (!is.element("readr", installed.packages()[, 1])) {
  install.packages("readr", dependencies = TRUE,
                   repos="https://cloud.r-project.org")
}
require("readr")
```

------------------------------------------------------------------------

**Note:** the following "*KnitR*" options have been set as the defaults in this markdown:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

------------------------------------------------------------------------

**Note:** the following "*R Markdown*" options have been set as the defaults in this markdown:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Loading the Student Performance Dataset

The 20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset is then loaded. The dataset and its metadata are available here: <https://drive.google.com/drive/folders/1-BGEhfOwquXF6KKXwcvrx7WuZXuqmW9q?usp=sharing>

```{r Load Dataset}
Student_dataset <-
  readr::read_csv(
                  "C:/Users/User/Documents/BBT4206-R-Lab2of15-ExploratoryDataAnalysis-Well-Beast/data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset - dataset (1).csv", # nolint
                  col_types =
                  readr::cols(
                              class_group =
                              readr::col_factor(levels = c("A", "B", "C")),
                              gender = readr::col_factor(levels = c("1", "0")),
                              YOB = readr::col_date(format = "%Y"),
                              regret_choosing_bi =
                              readr::col_factor(levels = c("1", "0")),
                              drop_bi_now =
                              readr::col_factor(levels = c("1", "0")),
                              motivator =
                              readr::col_factor(levels = c("1", "0")),
                              read_content_before_lecture =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              anticipate_test_questions =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              answer_rhetorical_questions =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              find_terms_I_do_not_know =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              copy_new_terms_in_reading_notebook =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              take_quizzes_and_use_results =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              reorganise_course_outline =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              write_down_important_points =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              space_out_revision =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              studying_in_study_group =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              schedule_appointments =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              goal_oriented =
                              readr::col_factor(levels =
                                                c("1", "0")),
                              spaced_repetition =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              testing_and_active_recall =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              interleaving =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              categorizing =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              retrospective_timetable =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              cornell_notes =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              sq3r = readr::col_factor(levels =
                                                       c("1", "2", "3", "4")),
                              commute = readr::col_factor(levels =
                                                          c("1", "2",
                                                            "3", "4")),
                              study_time = readr::col_factor(levels =
                                                             c("1", "2",
                                                               "3", "4")),
                              repeats_since_Y1 = readr::col_integer(),
                              paid_tuition = readr::col_factor(levels =
                                                               c("0", "1")),
                              free_tuition = readr::col_factor(levels =
                                                               c("0", "1")),
                              extra_curricular = readr::col_factor(levels =
                                                                   c("0", "1")),
                              sports_extra_curricular =
                              readr::col_factor(levels = c("0", "1")),
                              exercise_per_week = readr::col_factor(levels =
                                                                    c("0", "1",
                                                                      "2",
                                                                      "3")),
                              meditate = readr::col_factor(levels =
                                                           c("0", "1",
                                                             "2", "3")),
                              pray = readr::col_factor(levels =
                                                       c("0", "1",
                                                         "2", "3")),
                              internet = readr::col_factor(levels =
                                                           c("0", "1")),
                              laptop = readr::col_factor(levels = c("0", "1")),
                              family_relationships =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              friendships = readr::col_factor(levels =
                                                              c("1", "2", "3",
                                                                "4", "5")),
                              romantic_relationships =
                              readr::col_factor(levels =
                                                c("0", "1", "2", "3", "4")),
                              spiritual_wellnes =
                              readr::col_factor(levels = c("1", "2", "3",
                                                           "4", "5")),
                              financial_wellness =
                              readr::col_factor(levels = c("1", "2", "3",
                                                           "4", "5")),
                              health = readr::col_factor(levels = c("1", "2",
                                                                    "3", "4",
                                                                    "5")),
                              day_out = readr::col_factor(levels = c("0", "1",
                                                                     "2", "3")),
                              night_out = readr::col_factor(levels = c("0",
                                                                       "1", "2",
                                                                       "3")),
                              alcohol_or_narcotics =
                              readr::col_factor(levels = c("0", "1", "2", "3")),
                              mentor = readr::col_factor(levels = c("0", "1")),
                              mentor_meetings = readr::col_factor(levels =
                                                                  c("0", "1",
                                                                    "2", "3")),
                              `Attendance Waiver Granted: 1 = Yes, 0 = No` =
                              readr::col_factor(levels = c("0", "1")),
                              GRADE = readr::col_factor(levels =
                                                        c("A", "B", "C", "D",
                                                          "E"))),
                  locale = readr::locale())
```

## Description of the Dataset

We then display the number of observations and number of variables. We have 101 observations and 100 variables to work with.

```{r Your Fourth Code Chunk}
dim(Student_dataset)
```

Next, we display the quartiles for each numeric variable[*... this is the process of **"storytelling using the data."** The goal is to analyse the Student dataset and try to find a relation between the various variables and the exam mark( which variables or combination or variables affect the exam marks the most).*]{#highlight style="color: blue"}

```{r Your Fifth Code Chunk}
summary(Student_dataset)
```

# \<Measure of Mode of Writing down important point, and take quizzes and uses results\>

First we checked to see if the variable writing down important points, and take quizzes and use results were numeric. Next we measured the freqency of the outputs for this variable.

We found that a majority of the Students specifically 37.62% frequency of 4 and 37.62% frequency of 5 wrote down important notes and took quizzes and used results.

```{r Your Sixth Code Chunk}
sapply(Student_dataset, class) #For getting the data type.

Student_dataset_write_down_important_points_freq <- Student_dataset$write_down_important_points
cbind(frequency = table(Student_dataset_write_down_important_points_freq),
      percentage = prop.table(table(Student_dataset_write_down_important_points_freq)) * 100) #For getting frequency of writing down important points.

Student_dataset_take_quizzes_and_use_results_freq <- Student_dataset$take_quizzes_and_use_results
cbind(frequency = table(Student_dataset_take_quizzes_and_use_results_freq),
      percentage = prop.table(table(Student_dataset_take_quizzes_and_use_results_freq)) * 100) #For getting frequency of take quizzes and use results.



```

## \<measuring covariance \>
The Covariance of Write down important points is and that of Take quizzes and use results is 0.4099010

```{r Your Seventh Code Chunk}

```

## \<Measure the skewness of each variable\>
We proceeded to measure the skewness of the variables we chose to use for this dataset namely Write down important points, Reorganise course outline and Take quizzes and use results. Take quizzes and use results as well as Write down important points is negatively (left skew), whereas Recognise course outline is Symmetrical.
```{r Your Eighth Code Chunk}
if (!is.element("e1071", installed.packages()[, 1])) {
  install.packages("e1071", dependencies = TRUE)
}
require("e1071")
sapply (Student_dataset[, 12:14],  skewness, type = 2)

```

**etc.** as per the lab submission requirements. Be neat and communicate in a clear and logical manner.








